%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer - Merchant Control Center (MCC)}
    {ACI Worldwide}
    {Knysna, South Africa}
    {Nov. 2021 - Present}
    {
      \begin{cvitems}
        \item {Acted as the team's primary SME for our Angular 16 front-end stack, helping to onboard new Architect Engineers remotely working in Pune, India.}
        \item {Led the effort to implement and generate UI forms from JSON Schema specifications provided by our API.}
        \item {Initiated focus on improving end-to-end testing architecture using Cypress and Jenkins to improve the regression testing pipeline, and producing valuable artifacts for creating clear visibility of vulnerabilities and application defects.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Associate Software Engineer - Terminal Management System (TMS)}
    {ACI Worldwide}
    {Cape Town, South Africa}
    {Jun. 2019 - Oct. 2021}
    {
      \begin{cvitems}
        \item {Selected from a large pool of Engineers to conceive, design, and develop a state-of-the-art Terminal Management System SPA written in Angular and TypeScript, coupled with RESTful Docker micro-services using Springboot.
Adhered to strict Domain-Driven Design principles, emphasizing focus on on robustness, efficiency, scalability, and maintainability.}
        \item {Collaborated across multiple teams in the organization to produce a brand new software solution that maintains the integrity and congruence between the original legacy software solution and our new web-based solution.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Associate Software Engineer - PAX PED Development} % Job title
    {ACI Worldwide} % Organization
    {Cape Town, South Africa} % Location
    {Feb. 2019 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a new device driver functionality for PAX Pin Entry Devices, working closely with Product Owners and stakeholders to meet and exceed user and business requirements.}
      \end{cvitems}
    }
    
\end{cventries}
