%---------------------------------------------------------
\cvsection{Experience}
%---------------------------------------------------------

\begin{cventries}
  %---------------------------------------------------------
  \cventry{Software Engineer --- Merchant Control Center (MCC)}
  {ACI Worldwide}
  {Knysna, South Africa}
  {Nov. 2021 --- Present}
  {
    \begin{cvitems}
      \item {Spearheaded the implementation of dynamic UI forms generated from JSON Schema specifications provided by our API.}
      \item {
                  Pioneered enhancements to the end-to-end testing framework using Cypress and Jenkins, resulting in an improved
                  regression testing pipeline. This initiative also produced valuable artifacts for enhanced vulnerability and defect
                  tracking.
            }
      \item {
                  Acted as the user interface subject matter expert, facilitating remote onboarding for new Architect Engineer team members based in Pune,
                  India.
            }
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry{Associate Software Engineer --- Terminal Management System (TMS)}
  {ACI Worldwide}
  {Cape Town, South Africa}
  {Jun. 2019 --- Oct. 2021}
  {
    \begin{cvitems}
      \item {Handpicked to conceive, design, and develop a cutting-edge
                  Terminal Management System SPA using Angular and TypeScript, integrated
                  with RESTful Docker micro-services powered by Spring Boot.}
            {Strictly followed Domain-Driven Design principles, prioritizing
                  robustness, efficiency, scalability, and maintainability.}
      \item {Collaborated seamlessly across multiple teams to deliver a
                  seamless transition from legacy software to our modern web-based solution
                  while maintaining data integrity and consistency.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry{Associate Software Engineer --- PAX PED Development}
  {ACI Worldwide}
  {Cape Town, South Africa}
  {Feb. 2019 --- Jun. 2019}
  {
    \begin{cvitems}
      \item {- Innovated and delivered enhanced device driver
                  functionality for PAX Pin Entry Devices in collaboration with Product
                  Owners and stakeholders, surpassing user and business expectations.}
    \end{cvitems}
  }

\end{cventries}
